\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-12-06 manuscript.Rmd
*Conclusion
ggcorplot colours updated

ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90 )
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
```

@@

The overall we can concluded that IRT analysis indicated short form of LEBA is a psychometrically sound measure. Item fit indexes and person fit index for all five fitted model were acceptable. Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behavior. All-in-all we can recommend the short form of LEBA to be used to capture light exposure related behavior.

>>>>

ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90,colors = c("red", "white", "blue") )
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
```

@@

Overall we concluded that IRT analysis indicated short form of LEBA is a psychometrically sound measure. Item fit indexes and person fit index for all five fitted model were acceptable. Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behavior. All-in-all we can recommend the short form of LEBA to be used to capture light exposure related behavior.
